Balance responses in MS

### 2020-01-28 R/msBalance.Rmd
changed csv directory to tmp/

# if csv files do not exist, run matlab batch steps to populate them
if (!file.exists("../csv/c.csv")|!file.exists("../csv/m.csv")){
  system(paste(matlabCommand, "'cd ../m; loadData; exit'"))
}
```

@@

# load participant-level information
m = vroom("../csv/m.csv") %>% mutate(Group = "MS") %>% mutate(Age = round(age)) %>% mutate(Sex = toupper(gender)) %>% rename(Participant = Subj)
c = vroom("../csv/c.csv") %>% mutate(Group = "Control") %>% mutate(Age = round(age)) %>% mutate(Sex = toupper(gender)) %>% rename(Participant = Subj)

>>>>

# if csv files do not exist, run matlab batch steps to populate them
if (!file.exists("../csv/c.csv")|!file.exists("../tmp/m.csv")){
  system(paste(matlabCommand, "'cd ../m; loadData; exit'"))
}
```

@@

# load participant-level information
m = vroom("../tmp/m.csv") %>% mutate(Group = "MS") %>% mutate(Age = round(age)) %>% mutate(Sex = toupper(gender)) %>% rename(Participant = Subj)
c = vroom("../tmp/c.csv") %>% mutate(Group = "Control") %>% mutate(Age = round(age)) %>% mutate(Sex = toupper(gender)) %>% rename(Participant = Subj)
